On the probability of finding a nonphysical solution through shadowing

### 2020-10-22 main.tex
Add plucked tent map figures.

\begin{figure}
    \centering
    \includegraphics[width=0.35\textwidth,height=2in]{figure/mapn0s0.png}
    \includegraphics[width=0.35\textwidth,height=2in]{figure/mapn5s0.1.png}
    \caption{Two chaotic maps (in red) and their associated stationary  distributions (in purple). The map on the right is only an \emph{infinitesimal} perturbation of that on the left; for more information see \cite{desmos}.}
    \label{fig:map}
\end{figure}
[Nisha: shadowing perturabtions predict tiny effects. Real effect is a lot more dramatic. Desmos plot.]
% give example of numerics that destroys physicalness

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.35\textwidth,height=2in]{figure/osc_tent_n.png}
    \includegraphics[width=0.35\textwidth,height=2in]{figure/osc_tent_s.png}
    \caption{The plucked tent map shown at different values of $s$ and $n$, that represent the magnitude and frequency of the applied oscillation to the original tent map ($n=0,s=0$). On the left, $s$ is held constant at 0.5. On the right, $n$ is held constant at 0.}
    \label{fig:map}
\end{figure}
[Nisha: shadowing perturabtions predict tiny effects. Real effect is a lot more dramatic. Desmos plot.]
give example of numerics that destroys physicalness
